Thermodynamic fragments in magic state theories

### 2020-11-30 appendix.tex
added main text on LC

\subsection{Binomial distributions and error bounds}\label{app:phi}
Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
This scenario describes the construction of an $n$-copy Strange state Wigner distribution from a single-copy as presented in~\cref{sec:lcsu}.
The experiment is described by binomial statistics and we write down the sum over an even number of successful trials $\Phi_+$ (over an odd number of successful trials $\Phi_-$),
\begin{align}	
	\Phi_+(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}, \nonumber\\ 
	&\text{for even integers } \mmf\in[0,\nnf], \label{eq:fp_app} \\
	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
	&\text{for odd integers } \mmf\in[1,\nnf]. \label{eq:fn_app}
\end{align}
Note that index $\mmf$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of standard Lorenz curves.

@@

A useful result is the entropic bound on a combination~\cite{cit:ash}.
\begin{lemma}\label{lem:comb_bounds}
	For all $\mmf\in [1,\nnf-1]$,
	\begin{align}
		&\left[ 8\mmf\left(1-\frac{\mmf}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\mmf}{\nnf}\right)} \leq \binom{\nnf}{\mmf} \leq \\
		&\left[ 2\pi \mmf\left(1-\frac{\mmf}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\mmf}{\nnf}\right)}.
	\end{align}
\end{lemma}
\begin{proof}
	For $\mmf = 1,2, \nnf-1, \nnf-2$ check by direct calculation.	
	For all other cases, use Stirling's approximation. 
	\nick{CITE}
\end{proof}
With the help of this lemma, we directly arrive at 
\begin{theorem}\label{thm:bounds_strict}
	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_+(\mmf; \nnf, p) \geq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 16\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
		&\text{2. } \Phi_+(\mmf; \nnf, p) \leq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 4\pi\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
		&\text{3. } \Phi_-(\mmf; \nnf, p) \geq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 16(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd }\mmf\in [1,\nnf] \\
		&\text{4. } \Phi_-(\mmf; \nnf, p) \leq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 4\pi(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd } \mmf\in [1,\nnf]
		\end{split}
	\end{align*}
\end{theorem}
\begin{proof}
	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
\end{proof}

@@

>>>>

\subsection{Binomial distributions and error bounds}\label{app:phi}
Consider an experiment consisting of $n$ trials of throwing a $p$-coin, that is a coin with probability $p$ of landing on one side and $1-p$ of landing on the other.
This scenario describes the construction of an $n$-copy Strange state Wigner distribution from a single-copy as presented in~\cref{sec:lcsu}.
The experiment is described by binomial statistics and we write down the sum over an even number of successful trials $\Phi_+$ (over an odd number of successful trials $\Phi_-$),
\begin{align}	
	\Phi_+(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}, \nonumber\\ 
	&\text{for even integers } \mmf\in[0,\nnf], \label{eq:fp_app} \\
	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
	&\text{for odd integers } \mmf\in[0,\nnf]. \label{eq:fn_app}
\end{align}
Note that index $\mmf$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
In~\cref{app:lcsu_coord_elb}, we will use $\Phi_+$ and $\Phi_-$ to express the elbow coordinates of standard Lorenz curves.

@@

A useful result is the entropic bound on a combination~\cite{cit:ash}.
\begin{lemma}\label{lem:comb_bounds}
	For all $\dummy\in [1,\nnf-1]$,
	\begin{align}
		&\left[ 8\dummy\left(1-\frac{\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\dummy}{\nnf}\right)} \leq \binom{\nnf}{\dummy} \leq \\
		&\left[ 2\pi \dummy\left(1-\frac{\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{\nnf S\left(\frac{\dummy}{\nnf}\right)}.
	\end{align}
\end{lemma}
\begin{proof}
	For $\dummy = 1,2, \nnf-1, \nnf-2$ check by direct calculation.	
	For all other cases, use Stirling's approximation. 
	\nick{CITE}
\end{proof}
With the help of this lemma, we directly arrive at 
\begin{theorem}\label{thm:bounds_strict}
	Given fixed $n>0$ and $p$, $\Phi_+, \Phi_-$ satisfy the following bounds:
	\begin{align*}
		\begin{split}
		&\text{1. } \Phi_+(\mmf; \nnf, p) \geq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 16\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
		&\text{2. } \Phi_+(\mmf; \nnf, p) \leq \sum\limits_{\dummy=0}^{\mmf/2}\left[ 4\pi\dummy\left(1-\frac{2\dummy}{\nnf}\right) \right]^{-\frac{1}{2}} 2^{-\nnf\ent{\frac{2\dummy}{\nnf}}{p}}, \\
		&\hspace{14pt} \text{for all even } \mmf\in [2,\nnf] \\
		&\text{3. } \Phi_-(\mmf; \nnf, p) \geq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 16(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd }\mmf\in [1,\nnf] \\
		&\text{4. } \Phi_-(\mmf; \nnf, p) \leq \sum\limits_{\dummy=1}^{(\mmf-1)/2}\left[ 4\pi(\dummy+1)\left(1-\frac{2\dummy+1}{\nnf}\right) \right]^{-\frac{1}{2}} \times \\
		&\hspace{14pt} \times 2^{-\nnf\ent{\frac{2\dummy+1}{\nnf}}{p}},\ \text{for all odd } \mmf\in [1,\nnf]
		\end{split}
	\end{align*}
\end{theorem}
\begin{proof}
	All four statements follow from application of~\cref{lem:comb_bounds} on the combinatorial coefficient and the defintion of relative entropy given in~\cref{eq:ent_rel}
\end{proof}

@@

In particular, it can be used in the discussion of standard Lorenz curves to set the necessary constraints,
\begin{align}
L\left(x_{i'(0, \mlt'_{0}, 9^{\mm})}\right) &\geq L\left(x_{i'(0, m'_{0}, 9^{\mm})}\right), \nonumber\\
L\left(x_{i'(1, \mlt'_{1}, 9^{\mm})}\right) &\geq L\left(x_{i'(1, m'_{1}, 9^{\mm})}\right), \nonumber\\
&\vdotswithin{=} \nonumber\\
L\left(x_{i'(\tt, \mlt'_{r}, 9^{\mm})}\right) &\geq L\left(x_{i'(\tt, m'_{\tt}, 9^{\mm})}\right), \nonumber
\end{align}
where $x_{i'(0, \mlt'_{0}, 9^{\mm'})}, x_{i'(1, \mlt'_{1}, 9^{\mm'})}, \dots, x_{i'(\tt, \mlt'_{\tt}, 9^{\mm'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{\tt}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

### 2020-11-30 magic_paper.tex
added main text on LC

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,\tt$.
\end{theorem}
A proof is provided in~\cref{app:lc_constraints}.

@@

In~\cref{app:lcsu_technical}, we define explicit expressions for the Lorenz curve of the $n$-copy, $\epsilon$-noisy Strange state in the unital fragment, 
\begin{equation}\label{eq:lcsu}
	\lc{\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}}{\frac{1}{d}\id}(x),\ x\in[0,1].
\end{equation}
We call Lorenz curves of this type \emph{standard Lorenz curves}. \nick{expand (non-uniformity)}

It is clear in~\cref{fig:lcs} that Lorenz curves are fully defined by the coordinates of their elbows.
For standard Lorenz curves, elbow coordinates are defined in terms of the two functions,
\begin{align}	
	\Phi_+(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}, \nonumber\\ 
	&\text{for even integers } \mmf\in[0,\nnf], \label{eq:fp} \\
	\Phi_-(\mmf; \nnf, p) &\coloneqq \sum\limits_{\dummy=1}^{(\mmf-1)/2} \binom{\nnf}{2\dummy+1} p^{2\dummy+1} (1-p)^{\nnf-(2\dummy+1)}, \nonumber\\ 
	&\text{for odd integers } \mmf\in[1,\nnf]. \label{eq:fn}
\end{align}
Note that index $\mmf$ only takes even (odd) values when labelling $\Phi_+$ ($\Phi_-$).
The exact expresions depend on the noise level $\epsilon$, the parity of the number of copies $\NN$ and whether the location of the elbow relative to the curve maximum (LHS vs RHS).
All cases are presented in~\cref{tab:lcsu_coord_elb}.
\begin{table}[h]
  \def\arraystretch{1.5}
  \centering
  \begin{tabular}{c|c|c|r|r}
    \multicolumn{3}{c|}{Case} & \multicolumn{1}{c}{$x_{\ii}$} & \multicolumn{1}{|c}{$L_{\ii}$} \\[0.5ex]\hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$0\leq \epsilon < \frac{3}{7}$}}} & \hspace{0.8ex}\multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}}\hspace{0.8ex} & LHS & $\Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{1}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
    \multirow{4}{*}{\raisebox{-5ex}{\rotatebox[origin=c]{90}{$\frac{3}{7}\leq \epsilon < \frac{3}{4}$}}} & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ even}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\NN/2} + \Phi_-\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_-\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \cline{2-5}
    & \multirow{2}{*}{\raisebox{-3ex}{\rotatebox[origin=c]{90}{$\NN$ odd}}} & LHS & $\Phi_+\left(2\ii;\NN,\frac{1}{9}\right)$ & $\left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{3-4\epsilon}{15-8\epsilon}\right)$ \\
    & & RHS & $x_{\NN/2} + \Phi_+\left(2\ii;\NN,\frac{8}{9}\right)$ & $L_{\NN/2} - \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN\Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right)$ \\ \hline
  \end{tabular}
  \caption{Standard Lorenz curves elbow coordinates.
  Multiplication $2\ii$ is considered modulo $(\NN+1)$.
  Note that the Lorenz curve boundary points are $(x_{-1}, L_{-1}) \coloneqq (0,0)$ and $(x_{\NN}, L_{\NN}) = (1,1)$.
  }
  \label{tab:lcsu_coord_elb}
\end{table}

The coordinates of any point on the standard Lorenz curve is given by

\begin{equation}
    \II(\ii,\jj,\kk) \coloneqq \kk + \left[ (\jj-1) + \sum_{\dummy=0}^{\ii-1} 8^{2\dummy}\binom{\tt}{2\dummy} \right]9^{\mm},
\end{equation}

\begin{align}
    \II(\ii,\jj,\kk=1) &= \jj + \sum_{\dummy=0}^{\ii-1} 8^{2\dummy}\binom{\nn}{2\dummy}, \\
    \II'(\ii',\jj',\kk') &= \kk' + \left[ (\jj'-1) + \sum_{\dummy=0}^{\ii'-1} 8^{2\dummy}\binom{\tt}{2\dummy} \right]9^{\mm}.
\end{align}

In particular, it can used in the discussion of standard Lorenz curves to set the necessary constraints,
\begin{align}
\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon')\too{k}}{\frac{1}{d}\id}\left(x_{i'(0, m'_{0}, 9^{s})}\right), \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon')\too{k}}{\frac{1}{d}\id}\left(x_{i'(1, m'_{1}, 9^{s})}\right), \nonumber\\
&\vdotswithin{=} \nonumber\\
\lc{\noisysn}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right) &\geq \lc{\rho_{\rm{S}}(\epsilon')\too{k}}{\frac{1}{d}\id}\left(x_{i'(r, m'_{r}, 9^{s})}\right), \nonumber
\end{align}
where $x_{i'(0, m'_{0}, 9^{s'})}, x_{i'(1, m'_{1}, 9^{s'})}, \dots, x_{i'(r, m'_{r}, 9^{s'})} \in T$ are the locations of the elbows of $\lc{\rho_{\rm{S}}(\epsilon')\too{r}}{\frac{1}{d}\id}$ (excluding $0$ and $1$).

>>>>

	Then, $\lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x)$ for all $x \in [0,1]$ iff $\lc{\rho}{\sigma}(x_{\ii}) \geq \lc{\tau}{\sigma}(x_{\ii})$ for all $\ii =1,\dots,\tt$.
\end{theorem}
A proof is provided in~\cref{app:lc_constraints}.
Any of the $t$ inequalities in the theorem provides a valid contraint leading to some upper distillation bound, and the more one cosiders, the stricter the bound is.

@@

In~\cref{app:lcsu_technical}, we define explicit expressions for the Lorenz curve of the $\NN$-copy, $\epsilon$-noisy Strange state in the unital fragment, 
\begin{equation}\label{eq:lcsu}
	\lc{\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}}{\frac{1}{d}\id}(x),\ x\in[0,1].
\end{equation}
We call Lorenz curves of this type \emph{standard Lorenz curves}. \nick{expand (non-uniformity)}

Lorenz curves are fully defined by the coordinates of their elbows which is clear in~\cref{fig:lcs} for the Strange state in particular.
The exact expressions for the elbow coordinates of a standard Lorenz curve can take $2^3 = 8$ different forms, depending on whether the noise level $\epsilon$ is low/high, the parity of the number of copies $\NN$ is even/odd and the location of the elbow relative to the maximum is on the left hand side (LHS -- includes maximum) / right hand side (RHS).
They are given in full detail in~\cref{app:lcsu_coord_elb}.

Here we focus on the part of the process described by the LHS of the Lorenz curves, in low noise regimes ($0 \leq \epsilon < 3/7$) with even numbers of initial and target copies.
In this case, the elbow expressions of the standard Lorenz curve in~\cref{eq:lcsu} are given by
\begin{align}
	x_i &= \Phi_+\left(2\ii;\NN,\frac{8}{9}\right), \\
	L_i &= \left( \frac{5}{3} - \frac{8}{9}\epsilon\ \right)^\NN \Phi_+\left(2\ii;\NN,\frac{12-4\epsilon}{15-8\epsilon}\right),
\end{align}
for $i=0,\dots,\frac{\NN}{2}$, where
\begin{equation}
	\Phi_+(\mmf; \nnf, p) \coloneqq \sum\limits_{\dummy=0}^{\mmf/2} \binom{\nnf}{2\dummy} p^{2\dummy} (1-p)^{\nnf-2\dummy}.
\end{equation}
Conventionally, we set $(x_{-1}, L_{-1}) = (0,0)$.

The coordinates of any point on the Lorenz curve LHS can be expressed as convex sums of the neighbouring elbows,
\begin{align}
    x_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk}\right) x_{\ii-1} + p_{\ii\jj\kk} x_{\ii} \label{eq:lcsu_xcoord}\\
    L_{\ii\jj\kk} &= \left( 1-p_{\ii\jj\kk} \right) L_{\ii-1} + p_{\ii\jj\kk} L_{\ii}, \label{eq:lcsu_lcoord}
\end{align}
where we use a three-index parametrisation for the coordinates, with $\ii$ determined by the count of the elbow that follows, $\jj$ by the number of Strange state copies and $\kk$ by the number of tensored maximally mixed state copies.
Therefore, for the initial state $\noisysn$ we have
\begin{equation}
	p_{\ii\jj\kk} = \frac{\jj}{8^{2\ii}\binom{\nn}{2\ii}},
\end{equation}
with $\ii=0,\dots,\nn,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\nn}{2\ii}$ and $\kk = 1$.
For the target state $\noisys(\epsilon')\too{\tt} \otimes \left( \frac{1}{3}\id \right)\too{\mm}$,
\begin{equation}
	p_{\ii\jj\kk} = \frac{\kk + (\jj-1)9^{\mm}}{9^{\mm} 8^{2\ii}\binom{\tt}{2\ii}}
\end{equation}
with $\ii=0,\dots,\tt,\ \jj(\ii) = 1,\dots,8^{2\ii}\binom{\tt}{2\ii}$ and $\kk = 1,\dots,9^{\mm}$.
